A Theory for Data Migration of Information Systems

### 2022-10-15 2022 Migration/articleMigration.tex
working on the introduction

\section{Introduction}
\label{sct:Introduction}
   Data migration occurs when one stateful information system, $\infsys$, is replaced by another, $\infsys'$,
   while the data from $\infsys$ must be preserved.
   Agile teams today need to automate their data migrations, 
   as they do for all other activities in their software process.
   Teams continually automate to keep improving their performance without working any harder.
   They measure the effects in terms of DevOps metrics such as
   deployment frequency,
   reliability of deployments, and
   change failure rate~\cite{DevOps2021}.

   Data migrations can produce headaches, however.
   The challenge of data migration is to preserve the meaning of data
   rather than just copy the data from one place to another.
   Accumulated data pollution can pose extra complications.
   This makes data migrations far from trivial and a potential impediment for rapid and reliable deployment.

>>>>

\section{Introduction}
\label{sct:Introduction}
   The general aim of this work is to generate information systems incrementally, while in production.
   Our research focuses on generating information system,
   and specifically on the data migration aspect of it.
   The reason that we believe in generating information systems is to prevent human errors as early as possible in the build-chain:
   A mistake not made cannot propagate into production.

   Incremental generation of information systems poses specific requirements to data migration.
   For instance, if data migration is not for incremental generation,
   e.g.~\cite{Gholami2016,Bisbal1999},
   preserving the functionality can be useful to avoid introducing new errors in an otherwise error-prone process.
   For incremental generation, however, preserving the functionality is not an option.
   To change the functionality is the very purpose and the data migration must behave accordingly.
   So, we must make sure to use methods for data migration that are specifically meant for incrementally generating information systems.

   Data migration occurs when an as-is information system, $\infsys$, is replaced by a to-be information system, $\infsys'$,
   while preserving the meaning of the data from $\infsys$ as much as possible.
   Just copying the set of data from $\infsys$ to $\infsys'$ is clearly wrong if the schemas of both information systems differ.
   Information systems are typically used by distributed actors (both users and computers) who continually work with data.
   The entire set of data, $\dataset$, in an information system represents the state of the system.
   Every event that an actor causes may change the state $\dataset$.
   We will write $\dataset_{\infsys}$ in case we need to be specific about which information the dataset belongs to.

   In this work we will encode the semantics in a schema, $\schema$,
   so we can be explicit about "preserving the meaning as much as possible".
   The schema $\schema$ of an information system is basically a set of constraints on its dataset $\dataset$.
   Let us assume that information systems $\infsys$ and $\infsys'$ have different schemas
   because the task of migrating data is trivial if the schema doesn’t change.
   We will denote the schema of an information system $\infsys$ by $\schema_{\infsys}$
   if we need to be specific about the information system of which $\schema$ is the schema.

   We believe that information systems should be released into production in small increments,
   to obtain shorter release cycles, more frequent releases, and thus a more agile software development process%
   \footnote{The effects can be measured in terms of DevOps metrics such as
   deployment frequency,
   reliability of deployments, and
   change failure rate~\cite{DevOps2021}.}.
   And, if we want to deploy software updates more frequently, this requires updates with zero down-time.
   Extra complications arise from accumulated data pollution in the as-is information system.
   So, the theory we develop in this paper must lead to tools that satisfy such practical requirements as
   zero down-time updates and ways to cope with data pollution.
   That will help agile teams today to automate their software processes further.
